PoseIntelliGraph: Detecting Violence in Video Using Human Pose Graph Neural Networks\\

### 2025-05-17 paper.tex
chore: Update v0.1.0 of paper
Feat/paper v0.1.0 (#8)
* feat: Initi paper v0.1.0

* fix: Make sure figs with the width of the page

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

---------

Co-authored-by: Marc <marc.reyes@angkas.com>

@@

\section{Related Work}

\subsection{Violence Detection}
Violence detection in videos has been approached through various techniques over the years. Early methods relied on hand-crafted features like motion trajectories and spatiotemporal interest points \cite{nievas2011violence}. More recent approaches leverage deep learning, with CNN-based methods becoming prevalent. Sudhakaran and Lanz \cite{sudhakaran2017learning} proposed a combined CNN-LSTM architecture that captures both spatial and temporal aspects of violent actions. Wu et al. \cite{wu2020not} developed a system using 3D CNNs to capture motion characteristics specific to violent behavior.

@@

Training was performed on an NVIDIA RTX 3090 GPU with 24GB memory, taking approximately 4 hours to complete. We address the class imbalance problem by using weighted cross-entropy loss, where weights are inversely proportional to class frequencies.

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=1\textwidth]{CS28X-Student_Report_Latex_Template/New Project.jpg}
    \caption{MMPose-generated pose estimation with heatmap (left) Non-violent (right) Violent}
    \label{fig:enter-label}
\end{figure*}

@@

\section{Related Work}
\subsection{Violence Detection}
Violence detection in videos has been approached through various techniques
over the years. Early methods relied on hand-crafted features like motion
trajectories and spatiotemporal interest points \cite{nievas2011violence}. More
recent approaches leverage deep learning, with CNN-based methods becoming
prevalent. Sudhakaran and Lanz \cite{sudhakaran2017learning} proposed a
combined CNN-LSTM architecture that captures both spatial and temporal aspects
of violent actions. Wu et al. \cite{wu2020not} developed a system using 3D CNNs
to capture motion characteristics specific to violent behavior.

@@

Training was performed on an NVIDIA RTX A6000 GPU with 48GB memory, taking
approximately 47 hours to complete. We address the class imbalance problem by
using weighted cross-entropy loss, where weights are inversely proportional to
class frequencies.
